### 2016-06-29 GPCE2016/sections/Implementation.tex
Revised Section 4
Minor edits

\begin{figure*}[t]
\saveSpaceFig
\saveSpaceFig
\centering
\includegraphics[width=4.5in]{pdfs/screenshot4.png}
\caption{Generated methods shown in the Outline window of Eclipse and auto-completion.}
\label{fig:screenshot}
\saveSpaceFig
\end{figure*}

@@

Our automatic type refinement is a useful and convenient feature, but
not transparent to the heirs of the annotated interface.  They need to
be aware of the annotation semantics and provide the right type while
refining methods. To support heir coherence, we would need
to give up automatic type refinement, which is an essential part of IB programming.
However, the reader should note that Java libraries almost always break heir
coherence during evolution and still claim backward compatibility. In practice, adding any method to any
non-final class of a Java library is enough to break heir
coherence.  We think return type refinement breaks heir coherence ``less" than normal library evolution, and
if no automatic type-refinements are needed, then \mixin can claim a
form of heir coherence.
%Section~\ref{sec:translation} 
Formal definition/proofs for our safety claims are found in the
technical report.

>>>>

\begin{figure*}[t]
\saveSpaceFig
\saveSpaceFig
\centering
\includegraphics[width=5in]{pdfs/screenshot4.png}
\caption{Generated methods shown in the Outline window of Eclipse and auto-completion.}
\label{fig:screenshot}
\saveSpaceFig
\end{figure*}

@@

Our automatic type refinement is a useful and convenient feature, but
not transparent to the heirs of the annotated interface.  They need to
be aware of the annotation semantics and provide the right type while
refining methods. To support heir coherence, we need
to give up automatic type refinement, which is an essential part of IB programming.
However, Java libraries almost always break heir
coherence during evolution and still claim backward compatibility. In practice, adding any method to any
non-final class of a Java library is enough to break heir
coherence.  We think return type refinement breaks heir coherence ``less" than normal library evolution, and
if no automatic type-refinements are needed, then \mixin can claim a
form of heir coherence.
%Section~\ref{sec:translation} 
Formal definition/proofs for our safety claims are in the
technical report.
